Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-08-10 paper/paper-nature-revised.qmd
final updates

There are a wide variety of potential applications of this database. For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined). Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why. We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament. For instance, there is often concern that regional areas are overlooked compared with metropolitan areas. Again, our database could be used to examine whether this has changed over time. We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis. For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars. An international linkage provides a comparison case where domestic issues are different while international ones are common. As an example of enabling this linkage we have included PartyFacts IDs in our database. This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].

The Australian House of Representatives 'the House' performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. Politicians in the House are referred to as Members of Parliament (MPs). The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created (http://historichansard.net/). These data can be navigated by year, parliament, people, and bills. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created (https://github.com/palesl/AustralianHouseOfRepresentatives). Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed earlier, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed. In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website (https://partyfacts.herokuapp.com). Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/). Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the Usage Notes to follow. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` [@auspol] and `AustralianElections` R packages (https://github.com/RohanAlexander/AustralianElections). By including this variable, one can integrate our data records with those available in these two packages. Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.

>>>>

There are a wide variety of potential applications of this database. For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined). Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why. We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament. For instance, there is often concern that regional areas are overlooked compared with metropolitan areas. Again, our database could be used to examine whether this has changed over time. We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis. For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars. An international linkage provides a comparison case where domestic issues are different while international ones are common. As an example of enabling this linkage we have included PartyFacts IDs (https://partyfacts.herokuapp.com) in our database. This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].

The Australian House of Representatives, often referred to as 'the House', performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. Politicians in the House are referred to as Members of Parliament (MPs). The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created by Tim Sherratt (http://historichansard.net/). These data can be navigated by year, parliament, people, and bills. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created by Patrick Leslie (https://github.com/palesl/AustralianHouseOfRepresentatives). Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.

@@

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed earlier, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. This meant that we did not need to create lists of names and titles for which to search in the text as we did before. However, we used the same list of general interjection statements on which to separate as was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed. In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website. Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/). Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the Usage Notes to follow. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.

@@

To enhance the usability of our database, we added a `uniqueID` variable to each file. This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` R package, [@auspol] and the `AustralianElections` (https://github.com/RohanAlexander/AustralianElections) R package, which was created by Rohan Alexander. By including this variable, one can integrate our data records with those available in these two packages. Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.

### 2023-08-10 paper/paper-nature-revised.tex
final updates

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{August 8, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, frame hidden, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

There are a wide variety of potential applications of this database. For
instance, within Australia there is considerable concern that there has
been a decline in the `quality' of public policy debate (however that
might be defined). Our dataset could be used to look at whether it is
really getting worse in particular ways, and if so, why. We might also
be interested in whether particular sub-populations are appropriately
represented in what is talked about in parliament. For instance, there
is often concern that regional areas are overlooked compared with
metropolitan areas. Again, our database could be used to examine whether
this has changed over time. We have developed our database in such a way
that it could be linked with similar databases from other countries
which would enable comparative analysis. For instance, we may be
interested in how the policy focus of a parliament changes given various
global events such as pandemics or wars. An international linkage
provides a comparison case where domestic issues are different while
international ones are common. As an example of enabling this linkage we
have included PartyFacts IDs in our database. This should make it
possible to link our database with other large parliamentary speech
collection projects, such as ParlaMint\textsuperscript{4},
ParlSpeech\textsuperscript{5}, ParlEE\textsuperscript{6}, and
MAPLE\textsuperscript{7}.

The Australian House of Representatives `the House' performs a number of
crucial governmental functions, such as creating new laws and overseeing
government expenditure\textsuperscript{8, ch.~1}. Politicians in the
House are referred to as Members of Parliament (MPs). The House operates
under a parallel chamber setup, meaning there are two debate venues
where proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders\textsuperscript{8, ch.~8}. A
typical sitting day in the Chamber has a number of scheduled proceedings
including debates on government business, 90 second member statements,
and Question Time\textsuperscript{8, ch.~8}. The Federation Chamber was
created in 1994 as a subordinate debate venue of the Chamber. This
allows for better time management of House business as its proceedings
occur simultaneously with those of the Chamber\textsuperscript{8,
ch.~21}. Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members\textsuperscript{8, ch.~21}. It is the recording and compilation
of these proceedings on which Hansard is based, and it is essentially,
but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created
(http://historichansard.net/). These data can be navigated by year,
parliament, people, and bills. To make the Australian Parliamentary
Handbook more accessible, an \texttt{R} package which includes data on
all MPs from 1945 to 2019 has been created
(https://github.com/palesl/AustralianHouseOfRepresentatives). Further,
there is the \texttt{AustralianPoliticians} \texttt{R} package, which
contains several datasets related to the political and biographical
information of Australian federal politicians who were active between
1901 and 2021\textsuperscript{9}. And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{10}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
earlier, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml2},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. In other words, our approach to data cleaning in the third and
fourth scripts separated out interjections in the process. This meant
that we did not need to create lists of names and titles for which to
search in the text as we did before. However, we used the same list of
general interjection statements on which to separate as was used in the
first two scripts. We then did an additional check for statements that
may have not been separated due to how they were embedded in the XML,
and separated those out where needed. In particular, while most
statements were categorized in their own child node and hence captured
through pattern-based separation, some were not individually
categorized, and had to be split manually in this step.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag those rows where ``The House divided.'' was detected in the body
variable. The \texttt{gender} and \texttt{uniqueID} variables were added
based on the main dataset from the \texttt{AustralianPoliticians}
package, and the \texttt{partyfacts\_id} variable was added using code
and data provided by the Party Facts Project website
(https://partyfacts.herokuapp.com). Note that in accordance with the
code provided on the Party Facts downloads page
(https://partyfacts.herokuapp.com/download/), we used only the core
datasets maintained by the Party Facts project, which are the Manifesto
Project and ParlGov. Details on these datasets can be found on the Party
Facts datasets documentation page
(https://partyfacts.herokuapp.com/documentation/datasets/). Details on
the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
provided in the Usage Notes to follow. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. Lastly, the \texttt{order} variable was added to
maintain the order of proceedings, after all individual statements were
separated onto their own rows.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the
\texttt{AustralianPoliticians}\textsuperscript{9} and
\texttt{AustralianElections} R packages
(https://github.com/RohanAlexander/AustralianElections). By including
this variable, one can integrate our data records with those available
in these two packages. Similarly, we added the \texttt{partyfacts\_id}
variable to our data which allows users to link our data to external
political party data sources with this unique identifier.

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{August 10, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

There are a wide variety of potential applications of this database. For
instance, within Australia there is considerable concern that there has
been a decline in the `quality' of public policy debate (however that
might be defined). Our dataset could be used to look at whether it is
really getting worse in particular ways, and if so, why. We might also
be interested in whether particular sub-populations are appropriately
represented in what is talked about in parliament. For instance, there
is often concern that regional areas are overlooked compared with
metropolitan areas. Again, our database could be used to examine whether
this has changed over time. We have developed our database in such a way
that it could be linked with similar databases from other countries
which would enable comparative analysis. For instance, we may be
interested in how the policy focus of a parliament changes given various
global events such as pandemics or wars. An international linkage
provides a comparison case where domestic issues are different while
international ones are common. As an example of enabling this linkage we
have included PartyFacts IDs (https://partyfacts.herokuapp.com) in our
database. This should make it possible to link our database with other
large parliamentary speech collection projects, such as
ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.

The Australian House of Representatives, often referred to as `the
House', performs a number of crucial governmental functions, such as
creating new laws and overseeing government
expenditure\textsuperscript{8, ch.~1}. Politicians in the House are
referred to as Members of Parliament (MPs). The House operates under a
parallel chamber setup, meaning there are two debate venues where
proceedings take place: the Chamber, and the Federation Chamber.
Sittings of the House follow a predefined order of business, regulated
by procedural rules called standing orders\textsuperscript{8, ch.~8}. A
typical sitting day in the Chamber has a number of scheduled proceedings
including debates on government business, 90 second member statements,
and Question Time\textsuperscript{8, ch.~8}. The Federation Chamber was
created in 1994 as a subordinate debate venue of the Chamber. This
allows for better time management of House business as its proceedings
occur simultaneously with those of the Chamber\textsuperscript{8,
ch.~21}. Sittings in the Federation Chamber are different to those of
the Chamber in terms of their order of business and scope of discussion.
Business matters discussed in the Federation Chamber are limited largely
to intermediate stages of bill development, and the business of private
Members\textsuperscript{8, ch.~21}. It is the recording and compilation
of these proceedings on which Hansard is based, and it is essentially,
but not entirely, verbatim.

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created by Tim Sherratt
(http://historichansard.net/). These data can be navigated by year,
parliament, people, and bills. To make the Australian Parliamentary
Handbook more accessible, an \texttt{R} package which includes data on
all MPs from 1945 to 2019 has been created by Patrick Leslie
(https://github.com/palesl/AustralianHouseOfRepresentatives). Further,
there is the \texttt{AustralianPoliticians} \texttt{R} package, which
contains several datasets related to the political and biographical
information of Australian federal politicians who were active between
1901 and 2021\textsuperscript{9}. And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{10}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.

@@

Having developed a successful methodology for splitting interjections,
we used this to inform our general approach in the third and fourth
scripts. However, the difference in data cleaning used in these scripts
necessitated some departure from the original methodology. As discussed
earlier, we used string patterns extracted from
\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
As evident in Figure~\ref{fig-xml2},
\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
patterns of data from interjection statements were separated out in the
process. This meant that we did not need to create lists of names and
titles for which to search in the text as we did before. However, we
used the same list of general interjection statements on which to
separate as was used in the first two scripts. We then did an additional
check for statements that may have not been separated due to how they
were embedded in the XML, and separated those out where needed. In
particular, while most statements were categorized in their own child
node and hence captured through pattern-based separation, some were not
individually categorized, and had to be split manually in this step.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag those rows where ``The House divided.'' was detected in the body
variable. The \texttt{gender} and \texttt{uniqueID} variables were added
based on the main dataset from the \texttt{AustralianPoliticians}
package, and the \texttt{partyfacts\_id} variable was added using code
and data provided by the Party Facts Project website. Note that in
accordance with the code provided on the Party Facts downloads page
(https://partyfacts.herokuapp.com/download/), we used only the core
datasets maintained by the Party Facts project, which are the Manifesto
Project and ParlGov. Details on these datasets can be found on the Party
Facts datasets documentation page
(https://partyfacts.herokuapp.com/documentation/datasets/). Details on
the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
provided in the Usage Notes to follow. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. Lastly, the \texttt{order} variable was added to
maintain the order of proceedings, after all individual statements were
separated onto their own rows.

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} R
package,\textsuperscript{9} and the \texttt{AustralianElections}
(https://github.com/RohanAlexander/AustralianElections) R package, which
was created by Rohan Alexander. By including this variable, one can
integrate our data records with those available in these two packages.
Similarly, we added the \texttt{partyfacts\_id} variable to our data
which allows users to link our data to external political party data
sources with this unique identifier.
